\documentclass[11pt,a4paper,sans,colorlinks, urlcolor=black]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\moderncvhead{1}
\usepackage[scale=0.75, top=1cm, bottom=1cm]{geometry}
\usepackage{fontawesome5}
\firstname{Ashton}
\familyname{Sobeck}
\address{Greenville, SC}
\email{ashton@sobeck.dev}
\extrainfo{\faGithub \space \href{https://github.com/ashsobeck/}{github.com/ashsobeck}}
\nopagenumbers{}
\begin{document}	
	\vspace*{-2\baselineskip}
	\makecvtitle
	\vspace*{-3.3\baselineskip}
	\section{Education}
		\cventry{GPA: 3.75}{Clemson University}{M.S. Computer Science}{2022}{}{}
		\cventry{GPA: 3.90}{Clemson University}{B.S. Computer Science}{2018 - 2021}{}{}
	\section{Experience}
		\cventry{}{Workiva}{Software Engineer Intern}{Jan 2022 - Present}{}{}
		\cvlistitem{Created a robust performance testing framework that enhanced knowledge of the system's performance and led to a 33\% decrease in query execution time.} 
		\cvlistitem{Contributed to both frontend and backend features that provided our customers with an even better experience.}
		\cvlistitem{\textbf{Utilized:} Java, Dart, Python, SpringBoot, Locust Load Testing}

		\cventry{}{Clemson CCIT}{Cloud Engineer Intern}{May 2020 - December 2021}{}{}
		\cvlistitem{Utilized AWS CloudFormation, Lambda and scripts to help support the Atlassian suite to maximize availability and minimize costs.}
		\cvlistitem{Switched the QA environment to Spot Instances resulting in 25\% monthly costs savings.}
		\cvlistitem{\textbf{Utilized:} AWS, Lambda, CloudFormation, Python}

		\cventry{}{Infor}{DevOps Engineer Intern}{June 2021 - August 2021}{}{}
		\cvlistitem{Automated manual processes resulting in a time reduction of 70\% in deploying our software for customers.}
		\cvlistitem{Replicated existing architecture into CloudFormation templates for replicating across different environments.}
		\cvlistitem{\textbf{Utilized:} AWS, Lambda, CloudFormation, Python}
		\cventry{}{NIWC PAC}{Software Engineer Intern}{May 2020 - October 2020}{}{}
		\cvlistitem{Learned fundamental principles of frontend, backend, and API development.}
		\cvlistitem{Engaged in pair programming and other AGILE practices.}
		\cvlistitem{\textbf{Utilized:} ReactJS, ChakraUI, Java, SpringBoot}
	\section{Projects}
		\cvline{}{\textbf{Can PCA Reduce Dataset Size While Keeping Great CNN Performance?} \hfill \href{https://github.com/ashsobeck/cpsc8420finalproject}{\faGithub}}
		\cvlistitem{We wanted to see if applying PCA to the CIFAR10 dataset as an input to a CNN would produce satisfactory results while keeping the dataset size low}
		\cvlistitem{We used \textbf{Python} and \textbf{Keras} to create, train, and visualize the results from our models.}
		
		\cvlistitem{We found that compressing 81.25\% (6 of 32 principal components) of the data resulted in on par or just below image clasification performance of using the full dataset.}
		
		\cvline{}{\textbf{Melbourne Pedestrian Density}\hfill\href{https://github.com/ashsobeck/melbourne-pedestrian-visualization}{\faGithub}}
		\cvlistitem{Utilizing \textbf{deck.gl} and \textbf{d3.js}, we visualized the pedestrian density of Melbourne, Australia to show the busiest areas of the city at different times of the day.}
		\cvlistitem{We gave the user the option to compare different streets of Melbourne in which a comparative chart graphic would populate on the user's screen.}

		%\cvline{}{\textbf{Sobeck.dev} \hfill \href{https://github.com/ashsobeck/sobeck-dev-remix}{\faGithub}}
		%\cvlistitem{Created using the Remix framework, this hosts my portfolio and other projects I have.}
	
	\section{Skills}
		\cvline{Languages and Frameworks}{Dart, Java, ReactJS, Remix, TypeScript, YAML, Python, C/C++}
		\cvline{Other Skills}{AWS, AGILE, Git, Infrastructure as Code, Communication, Mentoring, APIs}
\end{document}